---
title: "Project Details"
params:
  output1: NA
  output2: NA
  output3: NA
  output4: NA
  output5: NA
  output6: NA
  output7: NA
  output8: NA
  output9: NA
  output10: NA
  output11: NA
  output_jur: NA
  output_apn: NA
  output_mit_names: NA
  output_screen_message: NULL
 # output_screen_type: NA
  output_length: NULL
  output_zone_id: NULL
  output_zone_sos: NULL 
  output_ite: NULL
  output_redev_vmt: NULL
  output_proposed_vmt: NULL
  output_redev_type: NULL
  output_analysis_type: NULL
  output_mu_lu_1: NULL
  output_mu_lu_2: NULL
  output_mu_lu_3: NULL
  output_mu_size1: NULL
  output_mu_size2: NULL
  output_mu_size3: NULL
  output_units: NA
  output_mitigated_vmt: NULL
  output_units1: NULL
  output_units2: NULL
  output_units3: NULL
  output_note: NA
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA)
library(formattable)
library(tidyverse)
library(scales)
```

```{r wrap-hook}

hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

The tool provides initial screening for all project types and more detailed analysis for residential, tourist accommodation unit, and public service projects.  All non-screened commercial, recreation, and other projects will need to complete a more detailed transportation analysis. For detailed information on the PIA  framework, tool usage, and calculations see the User Guidelines. For detailed information on the PIA  framework, tool usage, and calculations select the User Guidelines tab. For questions about the project impact assessment process contact Melanie Sloan (msloan@trpa.gov). For technical issues with the tool contact Reid Haefer (rhaefer@trpa.gov). 

## Date Submitted

```{r, echo=F}
cat(date())
```

## Report Notes

```{r, echo=F, linewidth=90}
cat(params$output_note)
```

## Analysis Type

```{r, echo=F, linewidth=90}
cat(params$output_analysis_type)
```

## Existing Land Use

```{r, echo=F}
cat(params$output_redev_type, "\n")
```

## Proposed Project

```{r, echo=F}
cat(params$output6, "\n")
cat(params$output7, "\n")
cat( paste(formattable::comma(params$output8,2), as.character(params$output_units)) , "\n")


cat(params$output_mu_lu_1, "\n")
cat(paste(as.character(formattable::comma(params$output_mu_size1,2)),as.character(params$output_units1)),"\n")


cat(params$output_mu_lu_2, "\n")
cat(paste(as.character(formattable::comma(params$output_mu_size2,2)),as.character(params$output_units2)),"\n")


cat(params$output_mu_lu_3, "\n")
cat(paste(as.character(formattable::comma(params$output_mu_size3,2)),as.character(params$output_units3)),"\n")


```

## VMT 

```{r, echo=F}
cat(
  paste(
  "Proposed Project Gross VMT", 
  as.character(formattable::comma(params$output_proposed_vmt,0)), sep=" - "), 
  "\n")

cat(
  paste(
  "Existing VMT", 
  as.character(formattable::comma(params$output_redev_vmt,0)), sep=" - "), 
  "\n")

cat(
  paste(
  "Mitigated VMT",
  as.character(formattable::comma(params$output_mitigated_vmt,0)), sep=" - "),
  "\n")

cat(
  paste(
  "Project Total Net VMT", 
  as.character(formattable::comma(params$output2,0)), sep=" - "), 
  "\n")

cat(
  paste(
  "Standard of Significance VMT", 
  as.character(formattable::comma(params$output3,0)), sep=" - "), 
  "\n")

cat(
  paste(
  "Mitigation Needed", 
  as.character(formattable::comma(params$output4,0)), sep=" - "), 
  "\n")
```

## Screening

```{r, echo=F}
cat(paste("Screened",params$output1, sep=" - "), "\n")
#cat("Screen Type",params$output_screen_type, "\n")
```

## Additional Analysis Required?

```{r, echo=F, linewidth=90}
cat(params$output_screen_message, "\n")
```

## Mitgation Info

```{r, echo=F, linewidth=90}

cat(paste("Mitigations",params$output_mit_names, sep=" - "), "\n")

cat(paste("Percent",params$output9, sep=" - "), "\n")
```

## Other Project Details

```{r, echo=F}
cat(paste("Zone ID",params$output_zone_id, sep=" - "), "\n")
cat(paste("Zone Average Trip Length",round(params$output_length,2), sep=" - "), "\n")
cat(paste("ITE Trip Rate (if applicable)",params$output_ite, sep=" - "), "\n")
cat(paste("Zone VMT Per Capita Standard of Significance",round(params$output_zone_sos,2), sep=" - "), "\n")
cat(paste("Located in Town/Regional Center",params$output10, sep=" - "), "\n")
cat(paste("Located in Bonus Unit Eligible Area",params$output11, sep=" - "), "\n")
cat(paste("Jurisdiction",params$output_jur, sep=" - "), "\n")
cat(paste("Parcel Number (APN)",params$output_apn, sep=" - "), "\n")
```





